### 2010-08-17 docs/mg/mg.tex
updated for eps_hg_bottom

  The final velocity projection uses a tolerance of $\epsilon = \min \{
  \mathtt{eps\_hg\_max}, \mathtt{eps\_hg} \cdot \mathtt{hg\_level\_factor}^{(\mathtt{nlevs} - 1)} \}$.  This tolerance
  is set in {\tt hgproject} using the parameter values specified in {\tt mg\_eps.f90}.  The default 
  parameter values are:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_hg}     &= $10^{-12}$ \\
   {\tt eps\_hg\_max}      &= $10^{-10}$ \\
   {\tt hg\_level\_factor}  &= 10 \\
   \end{tabular}
   \end{center}

>>>>

  The final velocity projection uses a tolerance of $\epsilon = \min \{
  \mathtt{eps\_hg\_max}, \mathtt{eps\_hg} \cdot \mathtt{hg\_level\_factor}^{(\mathtt{nlevs} - 1)} \}$.  This tolerance
  is set in {\tt hgproject} using the parameter values specified in {\tt mg\_eps.f90}.  A separate
  tolerance is used for the bottom
  solver, $\epsilon_\mathrm{bottom} = \mathtt{eps\_hg\_bottom}$.

  The default parameter values are:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_hg}     &= $10^{-12}$ \\
   {\tt eps\_hg\_max}      &= $10^{-10}$ \\
   {\tt hg\_level\_factor}  &= 10 \\
   {\tt eps\_hg\_bottom}   &= $10^{-4}$
   \end{tabular}
   \end{center}
